### 2016-03-25 paper3.tex
All figures on top of page.
All tables on top of page, rotated some of them.
Chapter intro-->background and using footnotes in titles

\chapter{Correcting for Telluric Absorption: Methods, Case Studies, and the TelFit Code}
\label{chap:telfit}
This chapter was previously published \citep{Gullikson2014}. Both co-authors were my advisor at some point while I was developing this code. They helped guide the code requirements and provided a science case study for the work. Adam Kraus provided observational data for the case study.

@@

\begin{table}
  \centering
  \caption{Observations used in this paper. }
  \begin{tabular}{|ccccccc|}
  \hline
    Star &    R   &  $\mathrm{K_s}$ & SpT  & UT date  & Spectrograph & SNR    \\
         &  (mag) & (mag)      &      & yyyymmdd &              & @820 nm \\ 
    \hline \hline

@@

\end{table}

@@

\begin{figure}
\begin{center}
\subfloat{\includegraphics[width=0.4\textwidth, height=0.23\textheight]{Figures/paper3_BstarCorr_590nm.pdf}} 
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_BstarCorr_650nm.pdf}}
\\
\noindent 
\subfloat{\includegraphics[width=0.4\textwidth, height=0.23\textheight]{Figures/paper3_BstarCorr_700nm.pdf}} 
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_BstarCorr_730nm.pdf}}
\caption{Correction of the water bands in optical spectra. All spectra are of the A0V star HIP 20264, and are smoothed with a Savitzky-Golay filter after telluric correction to remove any broad features in the stellar spectrum. The top panel of each figure shows the observed spectrum (black solid line) and the best-fit telluric model (red dashed line), and the bottom panel shows the residuals after division by the telluric model. The telluric water lines are corrected to very near the noise level of the spectrum in the top row, revealing weak interstellar Na D lines (top left). The telluric correction leaves residuals on the order of $5\%$ of the continuum for strong telluric lines (bottom right), possibly due to an incorrect atmosphere profile for water vapor.}

@@

\begin{figure}
\begin{center}
\subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_BstarCorr_630nm.pdf}}
\\ 
\subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_BstarCorr_690nm.pdf}}
\caption{Correction of the $\mathrm{O_2}$ bands in optical spectra. All spectra are of the A0V star HIP 20264, and are smoothed with a Savitzky-Golay filter after telluric correction to remove any broad features in the stellar spectrum. The top panel of each figure shows the observed spectrum (black solid line) and the best-fit telluric model (red dashed line), and the bottom panel shows the residuals after division by the telluric model. }

@@

\begin{figure}
\begin{center}
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_690nm.pdf}}
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_730nm.pdf}}
\\ 
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_LowSN_690nm.pdf}}
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_LowSN_730nm.pdf}}
\caption{Empirical telluric corrections. \emph{Top Row}: Correction at high S/N ratio, where all 7 frames of both the target star (HIP 20264, A0V) and the telluric standard star (HIP 25608, A1V) were co-added before the telluric correction. In this case, both the humidity and the airmass are changing throughout both exposures and the empirical telluric correction is very poor. \emph{Bottom Row}: Correction between the last frame taken of the target star and the first frame of the standard star, a more common mode of empirical correction. In this case, the empirical telluric correction is comparable to the model fitting method presented in this paper. The left column should be compared to the bottom panel in Figure \ref{paper3_fig:bstarcorr_oxygen}, and the right column should be compared to the bottom right subfigure in Figure \ref{paper3_fig:bstarcorr_water}. The poor correction in the oxygen band (lower left panel) is the result of the slight airmass difference between the science and standard stars. The correction in equation \ref{paper3_eqn:correction} is only valid for weak or moderate lines, and does not work as well for the nearly saturated lines shown here. The empirical correction under-corrects the line core while over-correcting the wings.}

@@

\begin{figure}[ht]
  \centering
  \subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_GJ908_Telluric.pdf}}
  \\
  \subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_GJ908_Stellar.pdf}}
  \caption{\emph{Top}: The observed spectrum of GJ 908 (black solid line) with the best-fit telluric spectrum (red dashed line) overplotted. There are telluric lines within the sodium doublet line profiles which affect any line shape measurements if they are not corrected. \emph{Bottom}: The telluric-corrected spectrum of GJ 908 (black solid line) with a PHOENIX model spectrum (red dashed line) overplotted to guide the eye. The model spectrum has the following parameters: $\mathrm{T_{eff}} = 3700 K$, $\log g = 4.0$, and $\mathrm{[Fe/H]} = -0.5$, and has been convolved with a gaussian to match the detector resolution. All of the remaining absorption lines in the spectrum come from the star.}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper3_SodiumLineProfile_BW.pdf}
  \caption{The evolution of the sodium doublet line profile with spectral type for a series of main-sequence M-type stars. The later spectral types show significantly broader line wings.}
  \label{paper3_fig:lineprofile}
\end{figure}

>>>>

\chapter{Correcting for Telluric Absorption: Methods, Case Studies, and the TelFit Code\footnote{
  This chapter was previously published \citep{Gullikson2014}. Both co-authors were my advisor at some point while I was developing this code. They helped guide the code requirements and provided a science case study for the work. Adam Kraus provided observational data for the case study.
}}
\label{chap:telfit}

@@

\afterpage{%
\begin{table}
  \centering
  \caption{Observations used in this paper. }
  \begin{tabular}{|ccccccc|}
  \hline
    Star &    R   &  $\mathrm{K_s}$ & SpT  & UT date  & Spectrograph & SNR    \\
         &  (mag) & (mag)      &      & yyyymmdd &              & @820 nm \\ 
    \hline \hline

@@

\end{table}
}

@@

\begin{figure}[t]
\begin{center}
\subfloat{\includegraphics[width=0.4\textwidth, height=0.23\textheight]{Figures/paper3_BstarCorr_590nm.pdf}} 
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_BstarCorr_650nm.pdf}}
\\
\noindent 
\subfloat{\includegraphics[width=0.4\textwidth, height=0.23\textheight]{Figures/paper3_BstarCorr_700nm.pdf}} 
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_BstarCorr_730nm.pdf}}
\caption{Correction of the water bands in optical spectra. All spectra are of the A0V star HIP 20264, and are smoothed with a Savitzky-Golay filter after telluric correction to remove any broad features in the stellar spectrum. The top panel of each figure shows the observed spectrum (black solid line) and the best-fit telluric model (red dashed line), and the bottom panel shows the residuals after division by the telluric model. The telluric water lines are corrected to very near the noise level of the spectrum in the top row, revealing weak interstellar Na D lines (top left). The telluric correction leaves residuals on the order of $5\%$ of the continuum for strong telluric lines (bottom right), possibly due to an incorrect atmosphere profile for water vapor.}

@@

\begin{figure}[t]
\begin{center}
\subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_BstarCorr_630nm.pdf}}
\\ 
\subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_BstarCorr_690nm.pdf}}
\caption{Correction of the $\mathrm{O_2}$ bands in optical spectra. All spectra are of the A0V star HIP 20264, and are smoothed with a Savitzky-Golay filter after telluric correction to remove any broad features in the stellar spectrum. The top panel of each figure shows the observed spectrum (black solid line) and the best-fit telluric model (red dashed line), and the bottom panel shows the residuals after division by the telluric model. }

@@

\begin{figure}[t]
\begin{center}
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_690nm.pdf}}
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_730nm.pdf}}
\\ 
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_LowSN_690nm.pdf}}
\subfloat{\includegraphics[width=0.4\textwidth,height=0.23\textheight]{Figures/paper3_Empirical_LowSN_730nm.pdf}}
\caption{Empirical telluric corrections. \emph{Top Row}: Correction at high S/N ratio, where all 7 frames of both the target star (HIP 20264, A0V) and the telluric standard star (HIP 25608, A1V) were co-added before the telluric correction. In this case, both the humidity and the airmass are changing throughout both exposures and the empirical telluric correction is very poor. \emph{Bottom Row}: Correction between the last frame taken of the target star and the first frame of the standard star, a more common mode of empirical correction. In this case, the empirical telluric correction is comparable to the model fitting method presented in this paper. The left column should be compared to the bottom panel in Figure \ref{paper3_fig:bstarcorr_oxygen}, and the right column should be compared to the bottom right subfigure in Figure \ref{paper3_fig:bstarcorr_water}. The poor correction in the oxygen band (lower left panel) is the result of the slight airmass difference between the science and standard stars. The correction in equation \ref{paper3_eqn:correction} is only valid for weak or moderate lines, and does not work as well for the nearly saturated lines shown here. The empirical correction under-corrects the line core while over-correcting the wings.}

@@

\begin{figure}[t]
  \centering
  \subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_GJ908_Telluric.pdf}}
  \\
  \subfloat{\includegraphics[height=0.33\textheight]{Figures/paper3_GJ908_Stellar.pdf}}
  \caption{\emph{Top}: The observed spectrum of GJ 908 (black solid line) with the best-fit telluric spectrum (red dashed line) overplotted. There are telluric lines within the sodium doublet line profiles which affect any line shape measurements if they are not corrected. \emph{Bottom}: The telluric-corrected spectrum of GJ 908 (black solid line) with a PHOENIX model spectrum (red dashed line) overplotted to guide the eye. The model spectrum has the following parameters: $\mathrm{T_{eff}} = 3700 K$, $\log g = 4.0$, and $\mathrm{[Fe/H]} = -0.5$, and has been convolved with a gaussian to match the detector resolution. All of the remaining absorption lines in the spectrum come from the star.}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper3_SodiumLineProfile_BW.pdf}
  \caption{The evolution of the sodium doublet line profile with spectral type for a series of main-sequence M-type stars. The later spectral types show significantly broader line wings.}
  \label{paper3_fig:lineprofile}
\end{figure}

### 2016-03-25 paper4.tex
All figures on top of page.
All tables on top of page, rotated some of them.
Chapter intro-->background and using footnotes in titles

\chapter{Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system}
\label{chap:psi1dra}
We now turn to our first case study in using the direct spectral detection method to find a faint companion to the bright star $\psi^1$ Draconis. in this chapter, we use archival data originally obtained in order to search for planetary companions. This chapter was previously published \citep{Gullikson2015}. The co-authors noticed a trend in the data, and suggested I look into it with the direct spectral detection methodology. They obtained the majority of the data used in the work.

@@

\begin{small}
\begin{longtable}{lrrrrrr}

@@

    \\ \hline
    Julian Date & \multicolumn{3}{c}{Primary RV (km/s)} & \multicolumn{3}{c}{Secondary RV (km/s)} \\
& raw & shifted & $\sigma$  & raw & shifted  & $\sigma$ \\ \hline
    \endhead

@@

\end{longtable}
\end{small}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Resid_CCFs.pdf}
  \caption{Cross-correlation functions of a 4400 K model spectrum template with the data, after subtraction of the average CCF. The dark curve in the top middle is the signal of the companion star.}
  \label{paper4_fig:resids}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Typical_CCF.pdf}
  \caption{An example of a typical residual cross-correlation function. The dominant peak denotes the template match of the 4400 K template with the companion to $\psi^1$ Draconis A. The velocities are in the approximate rest frame of the primary star (see text for details), and the centroid and FWHM are given as vertical dotted lines.}
  \label{paper4_fig:ccf_typical}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_corner.pdf}
  \caption{Marginalized posterior probability distribution estimates for the orbital parameters we fit. There is a strong degeneracy between the period and epoch of periastron ($T_0$) because we have not yet observed a full orbit.}
  \label{paper4_fig:posterior}
\end{figure}

\begin{table}
  \centering
\caption{The primary mass is derived using the spectroscopic $T_\mathrm{eff}$, $\log{g}$, and [Fe/H] and interpolating Dartmouth isochrones. The companion temperature is likewise derived from the companion mass using Dartmouth isochrones of the same metallicity.}
  \footnotesize
  \begin{tabular}{rl}
    \hline

@@

\begin{figure}

>>>>

\chapter{Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system\footnote{
  This chapter was previously published \citep{Gullikson2015}. The co-authors noticed a trend in the data, and suggested I look into it with the direct spectral detection methodology. They obtained the majority of the data used in the work.
}}
\label{chap:psi1dra}
We now turn to our first case study in using the direct spectral detection method to find a faint companion to the bright star $\psi^1$ Draconis. in this chapter, we use archival data originally obtained in order to search for planetary companions.

@@

\afterpage{%
\begin{small}
\begin{longtable}{lrrrrrr}

@@

    \caption{ - (Continued)} \\ \hline
    Julian Date & \multicolumn{3}{c}{Primary RV (km/s)} & \multicolumn{3}{c}{Secondary RV (km/s)} \\
& raw & shifted & $\sigma$  & raw & shifted  & $\sigma$ \\ \hline
    \endhead

@@

\end{longtable}
\end{small}
}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Resid_CCFs.pdf}
  \caption{Cross-correlation functions of a 4400 K model spectrum template with the data, after subtraction of the average CCF. The dark curve in the top middle is the signal of the companion star.}
  \label{paper4_fig:resids}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Typical_CCF.pdf}
  \caption{An example of a typical residual cross-correlation function. The dominant peak denotes the template match of the 4400 K template with the companion to $\psi^1$ Draconis A. The velocities are in the approximate rest frame of the primary star (see text for details), and the centroid and FWHM are given as vertical dotted lines.}
  \label{paper4_fig:ccf_typical}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_corner.pdf}
  \caption{Marginalized posterior probability distribution estimates for the orbital parameters we fit. There is a strong degeneracy between the period and epoch of periastron ($T_0$) because we have not yet observed a full orbit.}
  \label{paper4_fig:posterior}
\end{figure}

\begin{table}[t]
  \centering
\caption{The primary mass is derived using the spectroscopic $T_\mathrm{eff}$, $\log{g}$, and [Fe/H] and interpolating Dartmouth isochrones. The companion temperature is likewise derived from the companion mass using Dartmouth isochrones of the same metallicity.}
  \footnotesize
  \begin{tabular}{rl}
    \hline

@@

\begin{figure}[t]

### 2016-03-25 paper5.tex
All figures on top of page.
All tables on top of page, rotated some of them.
Chapter intro-->background and using footnotes in titles

\chapter{Direct Spectral Detection: An Efficient Method to Detect and Characterize Binary Systems}
\label{chap:dsd}
This chapter was previously published \citep{Gullikson2016}. Adam Kraus and Sarah Dodson-Robinson were both my advisors for part of the time that I spent developing the method outlined below. They provided much of the inspiration for the method and technical advice. Daniel Jaffe is the principal investigator for one of the instruments used in this work, the IGRINS spectrograph. The rest of the authors provided data that I used to calibrate the method.

\section{Introduction}
\label{paper5_sec:intro}

@@

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{paper5_fig:error:a}
            \includegraphics[scale=0.45]{Figures/paper5_TS23_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[HRS]{
             \label{paper5_fig:error:b}
             \includegraphics[scale=0.45]{Figures/paper5_HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{paper5_fig:error:c}
             \includegraphics[scale=0.45]{Figures/paper5_IGRINS_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[CHIRON]{
             \label{paper5_fig:error:d}
             \includegraphics[scale=0.45]{Figures/paper5_CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectral detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subpaper5_sec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{paper5_fig:error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper5_vsini_temperature_detection_rate_median.pdf}
  \caption{Median detection rate as a function of companion temperature and rotation speed. Each cell represents the median detection rate for targets with no detection in Table \ref{paper5_tab:known}. Companions represented by dark cells are detectable. See Section \ref{subpaper5_sec:sensitivity} for details of the analysis.}
  \label{paper5_fig:sensitivity_2d}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=80mm]{Figures/paper5_vsini_PDF.pdf}
    \caption{Typical probability density function for companion rotational velocity $v\sin{i}$. The distribution peaks near $\sim 5-10$ $\mathrm{km\ s}^{-1}$ and extends to very high velocities. Note that the x-axis is log-spaced to more clearly show the tails of the distribution.}
    \label{paper5_fig:vsini}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=80mm]{Figures/paper5_DetectionRate.pdf}

@@

\begin{figure*}
  \centering
  \subfigure[]{
       \label{paper5_fig:detections:a}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_13165+2013-08-14.pdf}
  }%
  \subfigure[]{
       \label{paper5_fig:detections:b}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_22958+2013-09-16.pdf}
  }

@@

  \caption{Cross-correlation functions for detected companions}
  \label{paper5_fig:detections}
\end{figure*}

\begin{figure*}
 \centering

@@

  \caption{Cross-correlation functions for detected companions}
  \label{paper5_fig:detections2}
\end{figure*}

@@

\begin{figure}
        \centering
        \includegraphics[width=80mm]{Figures/paper5_Known_Binaries.pdf}

@@

\begin{figure}
        \centering
        \includegraphics[width= 80mm]{Figures/paper5_HIP_88290_Flux.pdf}
         \caption{Observed (black) and expected (green) spectra for the known binary system HIP 88290. At the expected flux ratio, the spectral lines from the companion should be easily visible. }
         \label{paper5_fig:expected}
\end{figure}

@@

\begin{scriptsize}
\begin{longtable}{lllcccrcc}

@@

\begin{scriptsize}
\begin{longtable}{lcccccrccc}

@@

\begin{scriptsize}
\begin{longtable}{lcccccrccc}

@@

\begin{scriptsize}
\begin{longtable}{cccc}

@@

\begin{scriptsize}
\begin{longtable}{cccccccc}

>>>>

\chapter{Direct Spectral Detection: An Efficient Method to Detect and Characterize Binary Systems\footnote{
    This chapter was previously published \citep{Gullikson2016}. Adam Kraus and Sarah Dodson-Robinson were both my advisors for part of the time that I spent developing the method outlined below. Daniel Jaffe is the principal investigator for one of the instruments used in this work, the IGRINS spectrograph. The rest of the authors provided data that I used to calibrate the method.
}}
\label{chap:dsd}

\section{Background}
\label{paper5_sec:intro}

@@

\begin{figure}[t]
        \centering
        \subfigure[TS23]{
            \label{paper5_fig:error:a}
            \includegraphics[scale=0.45]{Figures/paper5_TS23_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[HRS]{
             \label{paper5_fig:error:b}
             \includegraphics[scale=0.45]{Figures/paper5_HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{paper5_fig:error:c}
             \includegraphics[scale=0.45]{Figures/paper5_IGRINS_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[CHIRON]{
             \label{paper5_fig:error:d}
             \includegraphics[scale=0.45]{Figures/paper5_CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectral detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subpaper5_sec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{paper5_fig:error}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper5_vsini_temperature_detection_rate_median.pdf}
  \caption{Median detection rate as a function of companion temperature and rotation speed. Each cell represents the median detection rate for targets with no detection in Table \ref{paper5_tab:known}. Companions represented by dark cells are detectable. See Section \ref{subpaper5_sec:sensitivity} for details of the analysis.}
  \label{paper5_fig:sensitivity_2d}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=80mm]{Figures/paper5_vsini_PDF.pdf}
    \caption{Typical probability density function for companion rotational velocity $v\sin{i}$. The distribution peaks near $\sim 5-10$ $\mathrm{km\ s}^{-1}$ and extends to very high velocities. Note that the x-axis is log-spaced to more clearly show the tails of the distribution.}
    \label{paper5_fig:vsini}
\end{figure}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=80mm]{Figures/paper5_DetectionRate.pdf}

@@

\begin{figure}[t]
  \centering
  \subfigure[]{
       \label{paper5_fig:detections:a}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_13165+2013-08-14.pdf}
  }%
  \subfigure[]{
       \label{paper5_fig:detections:b}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_22958+2013-09-16.pdf}
  }

@@

  \caption{Cross-correlation functions for detected companions}
  \label{paper5_fig:detections}
\end{figure}

\begin{figure}[t]
 \centering

@@

  \caption{Cross-correlation functions for detected companions}
  \label{paper5_fig:detections2}
\end{figure}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=80mm]{Figures/paper5_Known_Binaries.pdf}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width= 80mm]{Figures/paper5_HIP_88290_Flux.pdf}
         \caption{Observed (black) and expected (green) spectra for the known binary system HIP 88290. At the expected flux ratio, the spectral lines from the companion should be easily visible. }
         \label{paper5_fig:expected}
\end{figure}

@@

\clearpage
\afterpage{%
\begin{scriptsize}
\begin{longtable}{lllcccrcc}

@@

\end{longtable}
\end{scriptsize}
}

\clearpage
\afterpage{%
\begin{scriptsize}
\begin{longtable}{lcccccrccc}

@@

\end{longtable}
\end{scriptsize}
}

\newpage
\afterpage{%
\begin{scriptsize}
\begin{longtable}{lcccccrccc}

@@

\end{longtable}
\end{scriptsize}
}

\newpage
\afterpage{%
\begin{scriptsize}
\begin{longtable}{cccc}

@@

\end{longtable}
\end{scriptsize}
}

\clearpage
\newpage
\begin{scriptsize}
\begin{longtable}{cccccccc}

### 2016-03-25 paper6.tex
All figures on top of page.
All tables on top of page, rotated some of them.
Chapter intro-->background and using footnotes in titles

\section{Introduction}

\label{paper6_sec:intro}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{Figures/paper6_HIP_109139.pdf}
\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra. The detection at two dates shows significant velocity variation, indicating orbital motion with a short period. \emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature. The maxima of the curves indicate the temperature of the companion.}
\label{paper6_fig:ccf}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=4in]{Figures/paper6_Imaging_Data.pdf}
\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data. 
There are several nearby sources for HIP 88116, none of which are the source we detect in the 
spectroscopic data (see Section \ref{paper6_sec:companions}).}
\label{paper6_fig:images}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{Figures/paper6_PrimaryMassEstimates_log.pdf}
\caption{Comparison of primary star masses derived from our cross-correlation analysis and Padova isochrones \citep{Bressan2012} with those expected from the published spectral type. There is excellent agreement between the two measures across the entire range of masses.}
\label{paper6_fig:prim_mass}.
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{Figures/paper6_HIP_24244_20130919.pdf}
\caption{Detection rate as a function of companion temperature and $v\sin{i}$ for HIP 24244. All companions that are shaded yellow are detectable, while companions in the purple region are never detectable. The grids of squares in the lower left and upper right show the low temperature and high temperature grid points we used in the sensitivity analysis. The remaining squares come from assumptions about the shape of the detection rate surface and allow us to fully interpolate (see text for details).}
\label{paper6_fig:detrate_2d}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{Figures/paper6_HIP_24244_20130919_marginalized.pdf}
\caption{Marginalized detection rate for the same star as shown in Figure \ref{paper6_fig:detrate_2d}. The fall in detection rate towards hotter stars is caused by the increase in typical rotational speeds.}
\label{paper6_fig:marginalized}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{Figures/paper6_SurveyCompleteness.pdf}
\caption{Survey completeness as a function of mass ratio ($q$).}
\label{paper6_fig:completeness}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{Figures/paper6_MRD_total.pdf}
\caption{mass-ratio distribution for our sample. The data was fit to a histogram, a lognormal distribution, and a power law. The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars. The variance of the lognormal  fit is shown with 300 samples from the posterior probability distribution for the parameters in green. We also show the best-fit power law and the mass-ratio distribution resulting from random pairing of the Kroupa initial mass function. Finally, we display the raw mass ratio measurements with associated uncertainties in the cluster of data points near the top of the figure.}
\label{paper6_fig:mrd}
\end{figure}

@@

In the effort of open and reproducible research, we have made several data products freely available to the community. All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}. Samples of the primary and companion mass and system age posterior distributions are available at the same url, as are the posterior distributions for the parameters fit in Section \ref{paper6_sec:mrd}. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.

@@

\begin{tiny}
\begin{longtable}{|l|lrrrrllllll|}

@@

\end{longtable}
\end{tiny}

\begin{scriptsize}
\begin{longtable}{|l|rlrr|}

@@

\end{longtable}
\end{scriptsize}

\begin{tiny}
\begin{longtable}{|l|llllllll|}

    \caption{NIRI Observation log.}
    \\ \hline
      Star &  K &   date & Exposure & $\rho$ & $\theta$ & $\Delta \mathrm{K_c}$ & $M_2 (M_{\odot})$ & $a$ (AU)  \\ \hline
    \endfirsthead

@@

\end{longtable}
\end{tiny}

\begin{scriptsize}
\begin{longtable}{|l|rrlrrrll|}

    \caption{Companion Detections.}
    \\ \hline
       &  &  & Used in & $T_\mathrm{eff}$ & $v\sin{i}$ & [Fe/H] & \multicolumn{2}{c}{Mass ($M_{\odot}$)} \\ 
       Star & Component & $N_\mathrm{obs}$ & Analysis  &   (K) &   ($\mathrm{km\ s}^{-1}$) &  (dex) &  Isochrone &  Spectral Type \\ \hline
    \endfirsthead

@@

\end{longtable}
\end{scriptsize}

>>>>

\chapter{The Inner Mass-Ratio Distribution of Intermediate-Mass Stars\footnote{
    This chapter has been submitted for publication to the Astronomical Journal, but is not yet published.
}}
\label{chap:survey}

\section{Background}
\label{paper6_sec:intro}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{Figures/paper6_HIP_109139.pdf}
\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra. The detection at two dates shows significant velocity variation, indicating orbital motion with a short period. \emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature. The maxima of the curves indicate the temperature of the companion.}
\label{paper6_fig:ccf}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=4in]{Figures/paper6_Imaging_Data.pdf}
\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data. 
There are several nearby sources for HIP 88116, none of which are the source we detect in the 
spectroscopic data (see Section \ref{paper6_sec:companions}).}
\label{paper6_fig:images}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Figures/paper6_PrimaryMassEstimates_log.pdf}
\caption{Comparison of primary star masses derived from our cross-correlation analysis and Padova isochrones \citep{Bressan2012} with those expected from the published spectral type. There is excellent agreement between the two measures across the entire range of masses.}
\label{paper6_fig:prim_mass}.
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Figures/paper6_HIP_24244_20130919.pdf}
\caption{Detection rate as a function of companion temperature and $v\sin{i}$ for HIP 24244. All companions that are shaded yellow are detectable, while companions in the purple region are never detectable. The grids of squares in the lower left and upper right show the low temperature and high temperature grid points we used in the sensitivity analysis. The remaining squares come from assumptions about the shape of the detection rate surface and allow us to fully interpolate (see text for details).}
\label{paper6_fig:detrate_2d}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Figures/paper6_HIP_24244_20130919_marginalized.pdf}
\caption{Marginalized detection rate for the same star as shown in Figure \ref{paper6_fig:detrate_2d}. The fall in detection rate towards hotter stars is caused by the increase in typical rotational speeds.}
\label{paper6_fig:marginalized}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Figures/paper6_SurveyCompleteness.pdf}
\caption{Survey completeness as a function of mass ratio ($q$).}
\label{paper6_fig:completeness}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Figures/paper6_MRD_total.pdf}
\caption{mass-ratio distribution for our sample. The data was fit to a histogram, a lognormal distribution, and a power law. The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars. The variance of the lognormal  fit is shown with 300 samples from the posterior probability distribution for the parameters in green. We also show the best-fit power law and the mass-ratio distribution resulting from random pairing of the Kroupa initial mass function. Finally, we display the raw mass ratio measurements with associated uncertainties in the cluster of data points near the top of the figure.}
\label{paper6_fig:mrd}
\end{figure}

@@

In the effort of open and reproducible research, we have made several data products freely available to the community. All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}. Samples of the primary and companion mass and system age posterior distributions are available at \url{https://zenodo.org/record/48073}, as are the posterior distributions for the parameters fit in Section \ref{paper6_sec:mrd} and every cross-correlation function generated in our analysis. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.

@@

\begin{landscape}
\begin{scriptsize}
\begin{longtable}{|l|lrrrrlllll|}

@@

\end{longtable}
\end{scriptsize}
\end{landscape}

\newpage
\clearpage
\afterpage{%
\begin{scriptsize}
\begin{longtable}{|l|rlrr|}

@@

\end{longtable}
\end{scriptsize}
}

\clearpage
\begin{landscape}
\begin{scriptsize}
\begin{longtable}{|l|llllllll|}

    \caption{NIRI Observation log. \label{paper6_tab:imaging_obs}}
    \\ \hline
      Star &  K &   date & Exposure & $\rho$ & $\theta$ & $\Delta \mathrm{K_c}$ & $M_2 (M_{\odot})$ & $a$ (AU)  \\ \hline
    \endfirsthead

@@

\end{longtable}
\end{scriptsize}
\end{landscape}

\clearpage
\afterpage{%
\begin{scriptsize}
\begin{longtable}{|l|rrlrrrll|}

    \caption{Companion Detections. \label{paper6_tab:companions}}
    \\ \hline
       &  &  & Used in & $T_\mathrm{eff}$ & $v\sin{i}$ & [Fe/H] & \multicolumn{2}{c}{Mass ($M_{\odot}$)} \\ 
       Star & Component & $N_\mathrm{obs}$ & Analysis  &   (K) &   ($\mathrm{km\ s}^{-1}$) &  (dex) &  Isochrone &  Spectral Type \\ \hline
    \endfirsthead

@@

\end{longtable}
\end{scriptsize}
}
